The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-09-23 paper.tex
address Gregg's comments

\begin{abstract}
    A host of new low-frequency radio telescopes are attempting to detect the 21~cm transition at
    cosmological distances. These measurements hold promise to directly probe star and galaxy
    formation at redshifts $20 \gtrsim z \gtrsim 7$, but are limited by the dynamic range they can
    achieve against foreground sources of low-frequency radio emission. Consequently, there is a
    growing demand for modern, high-fidelity maps of the sky at frequencies below 200 MHz for use in
    foreground modeling and removal.  We use the Owens Valley Long Wavelength Array (OVRO-LWA) to
    generate 8 new maps of the sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution and
    at frequencies evenly spaced between 36.528 MHz and 73.152 MHz.  Existing full-sky maps at these
    frequencies have angular resolutions $\ge 2^\circ$ and so these maps are a 10-fold improvement
    in angular resolution.  The thermal noise in each map is $\sim$800 mJy/beam.  These maps are
    generated from the application of a new widefield imaging technique for drift-scanning
    interferometers, Tikhonov-regularized $m$-mode analysis imaging. This algorithm constructs
    images of the entire sky in a single synthesis imaging step with exact treatment of widefield
    effects. We additionally introduce this technique and describe how CLEAN can be adapted to
    deconvolve maps generated by $m$-mode analysis imaging.
\end{abstract}

@@

Current 21~cm cosmology experiments can be broadly separated into two classes: global experiments
that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm transition
after averaging over the entire sky (otherwise known as the monopole), and power spectrum
experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
of cosmological 21~cm perturbations.  Ongoing global experiments include EDGES
\citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA \citep{todo_price_2017}, BIGHORNS
\citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
\citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
\citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
\citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}.

Just as for CMB experiments, foreground removal or suppression is an essential component of both
classes of 21~cm cosmology experiments. The brightness temperature of the galactic synchrotron
emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
\begin{equation}
    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.5}\,.
\end{equation}
Therefore experiments conservatively need to achieve at least 4 orders of dynamic range against this
foreground emission before the cosmological signal can be measured. Current foreground removal
methods (for example, \citealt{2012ApJ...756..165P}) rely on the assumption that the foreground
emission (after convolving with the instrumental response) is spectrally smooth. However the
low-frequency radio sky is composed of several components: galactic synchrotron emission, supernova
remnants, radio galaxies, free-free emission and absorption from \ion{H}{2} regions, and a confusing
background of radio sources.  Ideally a foreground removal strategy should be informed by the
measured spatial structure and frequency spectrum of all foreground components.  This possibility is
limited by the availability of suitable high-fidelity low-frequency sky maps on angular scales
ranging from tens of degrees to arcminutes.

The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z} is currently the most
commonly used foreground model. The GSM is a data-driven interpolation of various maps between 10
MHz and 100 GHz. However the majority of information contained in the GSM is derived at frequencies
$>1.4$ GHz where the majority of the modern, high-fidelity input maps are located.  Below 408 MHz,
the GSM is largely driven by the Haslam 408 MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H,
2015MNRAS.451.4311R}. As a consequence, the GSM is not a faithful representation of the sky below
200 MHz. For instance, \citet{2017MNRAS.469.4537D} report errors of $\pm 50\%$ between the GSM and
their own maps at 74 MHz. This is largely due to the increasing contribution of free-free absorption
and modifications to the synchrotron spectral index at low frequencies.

Recently a host of new low-frequency sky surveys have been conducted including MSSS
\citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
\citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
catalog of radio point sources. Surveys that capture the diffuse emission include at 45 MHz, where
\citet{2011A&A...525A.138G} produced a map of the sky with 5$^\circ$ resolution, and the LWA1 Low
Frequency Sky Survey \citep{2017MNRAS.469.4537D}, which covers a range of frequencies between 35 MHz
and 80 MHz with resolution betwen 4.5$^\circ$ and 2$^\circ$.

This paper presents a series of new low-frequency maps of the sky between 36.528~MHz and 73.152~MHz,
capturing the full sky visible from the Owens Valley Radio Observatory (OVRO) with angular
resolution of $\sim 15$~arcmin. We aim for these maps to inform foreground removal strategies in
21~cm cosmology as they represent some of the highest angular resolution full-sky maps ever produced
at these frequencies. The maps will be made freely available online at the Legacy Archive for
Microwave Background Data Analysis (LAMBDA)\footnote{\url{https://lambda.gsfc.nasa.gov/}}.

@@

For a transit telescope, the visibilities $V^{ij}_\nu$ are a periodic function of sidereal
time.\footnote{
    This is not strictly true. Ionospheric fluctuations and non-sidereal sources (such as the sun)
    will violate this assumption. This paper will, however, demonstrate that the impact on the final
    maps is mild.
}
Therefore it is a natural operation to compute the Fourier transform of the visibilities with
respect to sidereal time $\phi\in[0,2\pi)$.
\begin{equation}
    V^{ij}_{m,\nu} = \int_0^{2\pi} V^{ij}_\nu(\phi)\exp\bigg(-im\phi\bigg)\,\d\phi
\end{equation}
The output of this Fourier transform is the set of $m$-modes $V^{ij}_{m,\nu}$ where
$m=0,\,\pm1,\,\pm2,\,\ldots$ is the Fourier conjugate variable to the sidereal time. The $m$-mode
corresponding to $m=0$ is a simple average of the visibilities over sidereal time. Similarly $m=1$
corresponds to the component of the visibilities that varies over half-day timescales. Larger values
of $m$ correspond to components that vary on quicker timescales.

@@

In practice we now need to pick the set of spherical harmonics we will use to represent the sky. For
an interferometer like the OVRO-LWA with lots of short baselines, a sensible choice is to use all
spherical harmonics with $l\le l_\text{max}$ for some $l_\text{max}$. The parameter $l_\text{max}$
is determined by the maximum baseline length of the interferometer.  For an interferometer without
short spacings, a minimum value for $l$ might also be used. This $l_\text{min}$ parameter should be
determined by the minimum baseline length.  When creating the maps presented in this paper, we use
$l_\text{min} = 0$ and $l_\text{max} = 1000$. %\todo{this choice of lmax restricts resolution at
%higher frequencies}

The interferometer's sensitivity to the monopole ($a_{00}$) deserves special consideration.
\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that a baseline with
nonzero sensitivity to $a_{00}$ must also have some amount of cross-talk or common-mode noise.  In
fact the sensitivity to $a_{00}$ is proportional to a sum of these effects. For example, one way a
baseline can have nonzero sensitivity to $a_{00}$ is if the baseline is extremely short. In this
case the antennas are so close together that voltage fluctuations in one antenna can couple into the
other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
measured and calibrated. Consequently we set $a_{00}=0$ in our analysis.

The size of a typical block in the transfer matrix is
$(2N_\text{base}N_\text{freq})\times(l_\text{max})$. If each element of the matrix is stored as a
64-bit complex floating point number, a single block is 500 MB for the case of single-channel
imaging with the OVRO-LWA. Compare this number with the 5 PB required for the naive approach.  The
power of $m$-mode analysis is the block-diagonal structure of
Equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
the computational complexity involved in inverting a single block is reduced by a factor of $N^3$
relative to a dense matrix. However we must invert $N$ blocks, so the overall computational savings
is proportional to $N^2$.  For the case of the OVRO-LWA the equation breaks up into $\sim10^3$
blocks and so we save a factor of $\sim10^6$ in processing time by using $m$-mode analysis.

@@

In traditional radio astronomy imaging, the CLEAN algorithm \citep{1974A&AS...15..417H} is used to
interpolate the measured visibilities onto the $uv$-plane. In the absence of this interpolation,
gaps in the interferometer's $uv$-coverage are assumed to be zero, and -- in the image plane --
sources are convolved with a point spread function (PSF) that is characteristic of the
$uv$-coverage.  Fundamentally, the interferometer's PSF in the dirty images is determined by which
modes were assumed to be zero in the initial imaging process.

@@

@@

The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
Owens Valley Radio Observatory near Big Pine, California \citep{todo_hallinan_2017}.  The OVRO-LWA
is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and
with 24 kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
hemisphere in a single snapshot image.  In the current configuration 32 antennas (64 signal paths)
are unused.

The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
snapshot imaging (see Figure~\ref{fig:antenna-layout}).  251 of the antennas are contained within a
200 m diameter core. 32 antennas are placed outside of the core in order to extend the maximum
baseline length to $\sim$1.5~km. The final 5 antennas are equipped with noise-switched front ends
for calibrated total power measurements of the global sky brightness.  These antennas are used as
part of the LEDA experiment \citep{todo_price_2017} to measure the global signal of 21~cm absorption
from the cosmic dawn.

@@

Antenna gain calibration is accomplished using an iterative method independently developed by
\citet{2008ISTSP...2..707M} and \citet{2014A&A...571A..97S}. The calibration routine is written in
the Julia programming language \citep{doi:10.1137/141000671}, and is publicly available
online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3 or
any later version).

Cyg~A and Cas~A are -- by an order of magnitude -- the brightest point-like radio sources in the
northern hemisphere. Therefore the optimal time to solve for the interferometer's gain calibration
is when these sources are at high elevations.  The antenna complex gains are measured from a 22
minute track of data from when Cyg~A and Cas are at high elevations. The gains measured in this way
are then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of
Cyg~A and Cas~A. The model flux of Cyg~A is set to the \citet{1977A&A....61...99B} spectrum while
the flux of Cas~A is measured from the data itself (using a preliminary calibration).  Residual
errors in the astrometry are corrected post-imaging by registering the images with respect to all
VLSSr \citep{2014MNRAS.440..327L} sources brighter than 30~Jy. Additional cuts are made to ensure
that sources aren't too close to each other or other bright sources.

@@

Small scale fluctuations are best characterized by source scintillation and refractive offsets.
Figure~\ref{fig:scintillation} shows the apparent flux and position offset of Cyg~A and Cas~A as a
function of time over the entire observing period. Both sources exhibit rapid scintillation on the
timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
A to have a measured flux of 30,000 Jy in one integration, and 20,000 Jy in the next. The measured
position offset of each source is a measurement of the ionospheric phase gradient across the array.
This varies on slower 10 minute timescales refracting each source by as much as 20 arcmin (at 36.528
MHz) from their true astronomical positions as waves in the ionosphere pass through the line of
sight. The impact of these effects on the sky maps is simulated in \S\ref{sec:ionosphere}.

@@

The sun can be trivially removed from any map of the sky by constructing the map using only data
taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
However the dataset used in this paper consists of 28 consecutive hours. Therefore we attempt to
suppress the contribution of the sun to the maps with the goal of suppressing its sidelobes.  The
sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the
optical depth $\tau=1$ surface of the sun changes with frequency and as a consequence a new model is
needed for each of the 8 channel maps produced in this paper. While we could fit a limited number of
Gaussian components to Cyg~A and Cas~A, this is insufficient for the Sun.  Additionally while most
astronomical sources at these frequencies have negative spectral indices, the Sun has a positive
spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
frequencies than at lower frequencies.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/spectral-index/internal-spectral-index}
    \caption{
        This Mollweide-projected map is constructed from 3 maps of the sky at 36.528~MHz (red),
        52.224~MHz (green), and 73.152~MHz (blue). The maps are scaled by $\nu^{2.5}$ before
        combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}). The
        local spectral index (estimated by means of a local T-T plot) is overlaid as a contour plot.
    }
    \label{fig:internal-spectral-index}
\end{figure*}

@@

In the first case, all sources at a given declination take the same path through the antenna primary
beam. If the antenna response is overestimated along this track then all sources at this declination
will have their flux underestimated. Similarly if the antenna response is underestimated then all
the sources will have their flux overestimated. The errors in Figure~\ref{fig:flux-scale} do not
show a clear pattern with declination. Two sources show a clear systematic error at all frequencies:
3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first southernmost
source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable declination to
Lyn A, which appears if anything to have its flux overestimated. The absence of a coherent pattern
doesn't eliminate the possibility of beam errors effecting the flux scale, but it does mean that
these errors are at least comparable to the errors inherent to the flux scale itself.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[height=0.32\textheight]{figures/haslam/haslam-spectral-index}
    \caption{
        The contours show the spectral index between the reprocessed Haslam 408 MHz map and the
        73.152 MHz map (degraded to 56 arcmin resolution). These contours are overlaid on the same
        3-color map as in Figure~\ref{fig:internal-spectral-index}. The regions with shallow
        spectral index between 73.152 MHz and 408 MHz coincide with regions with large free-free
        absorption that is evident between 36.528 MHz and 73.152 MHz.
    }
    \label{fig:haslam-spectral-index}
\end{figure*}

>>>>

\begin{abstract}
    A host of new low-frequency radio telescopes are attempting to detect the 21~cm transition at
    cosmological distances. These measurements hold promise to directly probe star and galaxy
    formation at redshifts $20 \gtrsim z \gtrsim 7$, but are limited by the dynamic range they can
    achieve against foreground sources of low-frequency radio emission. Consequently, there is a
    growing demand for modern, high-fidelity maps of the sky at frequencies below 200 MHz for use in
    foreground modeling and removal.  We use the Owens Valley Long Wavelength Array (OVRO-LWA) to
    generate 8 new maps of the sky north of $\delta=-30^\circ$ with 15 arcmin angular resolution and
    at frequencies evenly spaced between 36.528~MHz and 73.152~MHz with 24~kHz bandwidth.  Existing
    full-sky maps at these frequencies have angular resolutions $\ge 2^\circ$ and so these maps are
    a 10-fold improvement in angular resolution.  The thermal noise in each map is $\sim$800
    mJy/beam.  Future iterations will incorporate total power radiometry, and additional bandwidth
    and integration time. This will improve the thermal noise while simultaneously pushing to higher
    angular resolutions with the planned expansion of the OVRO-LWA to 2.6~km baselines. These maps
    are generated from the application of a new widefield imaging technique for drift-scanning
    interferometers, Tikhonov-regularized $m$-mode analysis imaging. This algorithm constructs
    images of the entire sky in a single synthesis imaging step with exact treatment of widefield
    effects. We additionally introduce this technique and describe how CLEAN can be adapted to
    deconvolve maps generated by $m$-mode analysis imaging.  These maps serve as a first step on the
    path to the use of more sophisticated foreground filters in 21~cm cosmology incorporating the
    measured angular and frequency structure of all foreground contaminants.
\end{abstract}

@@

Current 21~cm cosmology experiments can be broadly separated into two classes: global experiments
that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm transition
after averaging over the entire sky (otherwise known as the monopole), and power spectrum
experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
of cosmological 21~cm perturbations.  Ongoing global experiments include EDGES
\citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA \citep{price_2017}, BIGHORNS
\citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
\citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
\citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
\citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}.

Just as for CMB experiments, foreground removal or suppression is an essential component of both
classes of 21~cm cosmology experiments. The brightness temperature of the galactic synchrotron
emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
\begin{equation}
    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.5}\,.
\end{equation}
Therefore experiments conservatively need to achieve 5 orders of dynamic range against this
foreground emission before the cosmological signal can be measured. Current foreground removal
methods (for example, \citealt{2012ApJ...756..165P}) rely on the assumption that the foreground
emission is spectrally smooth. However the low-frequency radio sky is composed of several
components: galactic synchrotron emission, supernova remnants, radio galaxies, free-free emission
and absorption from \ion{H}{2} regions, and a confusing background of radio sources.  Ideally a
foreground removal strategy should be informed by the measured spatial structure and frequency
spectrum of all foreground components.  This possibility is limited by the availability of suitable
high-fidelity low-frequency sky maps on angular scales ranging from tens of degrees to arcminutes.

The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z} is currently the most
commonly used foreground model. The GSM is a data-driven interpolation of various maps between 10
MHz and 100 GHz. However the majority of information contained in the GSM is derived at frequencies
$>1.4$ GHz where the majority of the modern, high-fidelity input maps are located.  Below 408 MHz,
the GSM is a strong function of the Haslam 408 MHz map \citep{1981A&A...100..209H,
1982A&AS...47....1H, 2015MNRAS.451.4311R}. As a consequence, the GSM is not a faithful
representation of the sky below 200 MHz. For instance, \citet{2017MNRAS.469.4537D} report errors of
$\pm 50\%$ between the GSM and their own maps at 74 MHz. This is largely due to the increasing
contribution of free-free absorption and modifications to the synchrotron spectral index at low
frequencies.

Recently a host of new low-frequency sky surveys have been conducted including MSSS
\citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
\citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
catalog of radio point sources. At 45 MHz, \citet{2011A&A...525A.138G} created a map of the sky that
captures the diffuse emission with 5$^\circ$ resolution.  The LWA1 Low Frequency Sky Survey
\citep{2017MNRAS.469.4537D} similarly maps the sky at a range of frequencies between 35~MHz and
80~MHz with resolution between 4.5$^\circ$ and 2$^\circ$.

This paper presents a series of new low-frequency maps of the sky between 36.528~MHz and 73.152~MHz,
capturing the full sky visible from the Owens Valley Radio Observatory (OVRO) with angular
resolution of $\sim 15$~arcmin. We aim for these maps to inform foreground removal strategies in
21~cm cosmology as they represent some of the highest angular resolution full-sky maps ever produced
at these frequencies. We anticipate additional anciliary science taking advantage of the combination
of high fidelity and high resolution of these maps, including but not limited to studies of the
cosmic ray emissivity at low frequencies, searches for giant radio galaxies, and constraining the
galactic synchrotron spectrum. The maps will be made freely available online at the Legacy Archive
for Microwave Background Data Analysis (LAMBDA)\footnote{\url{https://lambda.gsfc.nasa.gov/}}.

@@

For a transit telescope, the visibilities $V^{ij}_\nu$ are a periodic function of sidereal
time.\footnote{
    This is not strictly true. Ionospheric fluctuations and non-sidereal sources (such as the Sun)
    will violate this assumption. This paper will, however, demonstrate that the impact on the final
    maps is mild.
}
Therefore it is a natural operation to compute the Fourier transform of the visibilities with
respect to sidereal time $\phi\in[0,2\pi)$.
\begin{equation}
    V^{ij}_{m,\nu} = \int_0^{2\pi} V^{ij}_\nu(\phi)\exp\bigg(-im\phi\bigg)\,\d\phi
\end{equation}
The output of this Fourier transform is the set of $m$-modes $V^{ij}_{m,\nu}$ where
$m=0,\,\pm1,\,\pm2,\,\ldots$ is the Fourier conjugate variable to the sidereal time. The $m$-mode
corresponding to $m=0$ is a simple average of the visibilities over sidereal time. Similarly $m=1$
corresponds to the component of the visibilities that varies over half-day timescales. Larger values
of $m$ correspond to components that vary on quicker timescales.

@@

In practice we now need to pick the set of spherical harmonics we will use to represent the sky. For
an interferometer like the OVRO-LWA with lots of short baselines, a sensible choice is to use all
spherical harmonics with $l\le l_\text{max}$ for some $l_\text{max}$. The parameter $l_\text{max}$
is determined by the maximum baseline length of the interferometer.  For an interferometer without
short spacings, a minimum value for $l$ might also be used. This $l_\text{min}$ parameter should be
determined by the minimum baseline length. A rough estimate of $l$ for a baseline of length $b$ at
frequency $\nu$ is $l \sim \pi b\nu/c$. For the OVRO-LWA we therefore adapt $l_\text{min}=0$ and
$l_\text{max}=1000$ across all frequencies. However this choice of $l_\text{max}$ actually limits
the angular resolution above 55~MHz, and therefore future work will increase $l_\text{max}$ to
obtain better angular resolution.

The interferometer's sensitivity to the monopole ($a_{00}$) deserves special consideration.
\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that a baseline with
nonzero sensitivity to $a_{00}$ must also have some amount of cross-talk or common-mode noise.  In
fact the sensitivity to $a_{00}$ is proportional to a sum of these effects. For example, one way a
baseline can have nonzero sensitivity to $a_{00}$ is if the baseline is extremely short. In this
case the antennas are so close together that voltage fluctuations in one antenna can couple into the
other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
measured and calibrated. Consequently we set $a_{00}=0$ in our analysis. In the future this will be
addressed with the inclusion of calibrated total power radiometry.

The size of a typical block in the transfer matrix is
$(2N_\text{base}N_\text{freq})\times(l_\text{max})$. If each element of the matrix is stored as a
64-bit complex floating point number, a single block is 500 MB for the case of single-channel
imaging with the OVRO-LWA, which a modern computer can easily store and manipulate in memory.  The
power of $m$-mode analysis is the block-diagonal structure of
Equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
the computational complexity involved in inverting a single block is reduced by a factor of $N^3$
relative to a dense matrix. However we must invert $N$ blocks, so the overall computational savings
is proportional to $N^2$.  For the case of the OVRO-LWA the equation breaks up into $\sim10^3$
blocks and so we save a factor of $\sim10^6$ in processing time by using $m$-mode analysis.

@@

In traditional radio astronomy imaging, the CLEAN algorithm \citep{1974A&AS...15..417H} is used to
interpolate between measured visibilities on the $uv$-plane. In the absence of this interpolation,
gaps in the interferometer's $uv$-coverage are assumed to be zero, and -- in the image plane --
sources are convolved with a point spread function (PSF) that is characteristic of the
$uv$-coverage.  Fundamentally, the interferometer's PSF is determined by which modes were assumed to
be zero in the initial imaging process.

@@

In summary, Tikhonov-regularized $m$-mode analysis imaging constructs a widefield synthesis image of
the sky from a complete earth rotation, and  with exact treatment of widefield-effects. This is
accomplished by solving a regularized block-diagonal matrix equation
(Equation~\ref{eq:tikhonov-solution}). The solution to this equation generates a map where
sources are convolved with a PSF characteristic of the interferometer (a function of the frequency,
antenna response, and baseline distribution with a full Earth rotation). The CLEAN algorithm is
adopted to deconvolve the PSF and produce the final sky maps.

@@

The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
Owens Valley Radio Observatory near Big Pine, California \citep{hallinan_2017}.  The OVRO-LWA
is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and
with 24 kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
hemisphere in a single snapshot image.  In the current configuration 32 antennas (64 signal paths)
are unused.

The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
snapshot imaging (see Figure~\ref{fig:antenna-layout}).  251 of the antennas are contained within a
200 m diameter core. 32 antennas are placed outside of the core in order to extend the maximum
baseline length to $\sim$1.5~km. The final 5 antennas are equipped with noise-switched front ends
for calibrated total power measurements of the global sky brightness.  These antennas are used as
part of the LEDA experiment \citep{price_2017} to measure the global signal of 21~cm absorption from
the cosmic dawn. A final stage of construction will involve 64 antennas installed on long baselines
out to a maximum length of 2.6~km.

@@

Antenna gain calibration is accomplished using alternating least squares otherwise known as
``stefcal'' \citep{2008ISTSP...2..707M, 2014A&A...571A..97S}.  \citet{2008ISTSP...2..707M} and
\citet{2014A&A...571A..97S}. The calibration routine is written in the Julia programming language
\citep{doi:10.1137/141000671}, and is publicly available
online\footnote{\url{https://github.com/mweastwood/TTCal.jl}} under an open source license (GPLv3 or
any later version).

Cyg~A and Cas~A are -- by an order of magnitude -- the brightest point-like radio sources in the
northern hemisphere. Therefore the optimal time to solve for the interferometer's gain calibration
is when these sources are at high elevations.  The antenna complex gains are measured from a 22
minute track of data from when Cyg~A and Cas are at high elevations. The gains measured in this way
are then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of
Cyg~A and Cas~A. The model flux of Cyg~A is set to the \citet{1977A&A....61...99B} spectrum while
the flux of Cas~A is measured from the data itself (using a preliminary calibration).  Residual
errors in the astrometry are corrected post-imaging by registering the images with respect to all
VLSSr \citep{2014MNRAS.440..327L} sources brighter than 30~Jy. Additional cuts are made to ensure
that sources aren't too close to each other or other bright sources, and that the VLSSr flux density
matches is consistent with the flux density measured by the OVRO-LWA.

@@

Small scale fluctuations are best characterized by source scintillation and refractive offsets.
Figure~\ref{fig:scintillation} shows the apparent flux and position offset of Cyg~A and Cas~A as a
function of time over the entire observing period. Both sources exhibit rapid scintillation on the
timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
A to have a measured flux variations of 50\% between adjacent 13 second integrations.  The measured
position offset of each source is a measurement of the ionospheric phase gradient across the array.
This varies on slower 10 minute timescales refracting each source by as much as 20 arcmin (at 36.528
MHz) from their true astronomical positions as waves in the ionosphere pass through the line of
sight. The impact of these effects on the sky maps is simulated in \S\ref{sec:ionosphere}.

@@

The Sun can be trivially removed from any map of the sky by constructing the map using only data
taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
However the dataset used in this paper consists of 28 consecutive hours. Therefore we attempt to
suppress the contribution of the Sun to the maps with the goal of suppressing its sidelobes.  The
Sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the
optical depth $\tau=1$ surface of the Sun changes with frequency and as a consequence a new model is
needed for each of the 8 channel maps produced in this paper. While we could fit a limited number of
Gaussian components to Cyg~A and Cas~A, this is insufficient for the Sun.  Additionally while most
astronomical sources at these frequencies have negative spectral indices, the Sun has a positive
spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
frequencies than at lower frequencies.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/spectral-index/ovro-lwa-sky-map.pdf}
    \caption{
        This Mollweide-projected map is constructed from 3 maps of the sky at 36.528~MHz (red),
        52.224~MHz (green), and 73.152~MHz (blue). The maps are scaled by $\nu^{2.5}$ before
        combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}).
    }
    \label{fig:three-color}
\end{figure*}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/spectral-index/internal-spectral-index}
    \caption{
        This plot shows the local spectral index (estimated by means of a local T-T plot) as a
        contour plot. The contours are overlaid on the three-color image from
        Figure~\ref{three-color}.
    }
    \label{fig:internal-spectral-index}
\end{figure*}

@@

In the first case, all sources at a given declination take the same path through the antenna primary
beam. If the antenna response is overestimated along this track then all sources at this declination
will have their flux underestimated. Similarly if the antenna response is underestimated then all
the sources will have their flux overestimated. The errors in Figure~\ref{fig:flux-scale} do not
show a clear pattern with declination. Two sources show a clear systematic error at all frequencies:
3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first southernmost
source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable declination to
Lyn A, which appears, if anything, to have its flux overestimated. The absence of a coherent pattern
doesn't eliminate the possibility of beam errors effecting the flux scale, but it does mean that
these errors are at least comparable to the errors inherent to the flux scale itself. On the other
hand, the spectral indices presented in Figure~\ref{fig:internal-spectral-index} are systematically
flatter from declinations between $-20^\circ$ and $-30^\circ$. This indicates the existence of beam
errors at elevations $\lesssim20^\circ$.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[height=0.32\textheight]{figures/haslam/haslam-spectral-index}
    \caption{
        The contours show the spectral index between the reprocessed Haslam 408 MHz map and the
        73.152 MHz map (degraded to 56 arcmin resolution). These contours are overlaid on the same
        three-color map from Figure~\ref{fig:three-color}. The regions with shallow spectral index
        between 73.152 MHz and 408 MHz coincide with regions with large free-free absorption that is
        evident between 36.528 MHz and 73.152 MHz.
    }
    \label{fig:haslam-spectral-index}
\end{figure*}
